\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{Accelerator Science and Technology Centre\\Daresbury Science \& Innovation Campus\\Daresbury\\Warrington\\Cheshire\\WA4 4AD}

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{To whom it may concern,} 

I am writing this letter to express my interest in Summer Internship by STFC. Applying to ASTeC directly as I believe it coincide with my goal of becoming an experimental physicist. I am always fascinated and interested in particle accelerator as the research topic revolves around it always excites me. Although theoretical physics maybe a much better choice but just working on the mathematical model alone does not justify the physics in my opinion. Experiment such as LHC and T2K are the kind of work i would be interested in the future and learning physics in this way would be much more exciting.

The last semester, i had to do a personal dissertation on the topic on Neutrino Oscillation. This allowed me to learn new way of finding resources through academic journals. During the course of writing the dissertation, i learned various way of detecting Neutrino that some experiment such as T2K uses. This also allowed me to expand my knowledge on physics beyond the Standard Model and learning some unsolved problem in physics.  

The previous placement I did was with Oxford Instruments at Tubney Woods for 8 weeks Through a SEPnet summer placement program. The work I did for the placement were later exhibited at a SEPnet Student Expo in Nov 2014. During the 8 week placement, i was task with designing a experiment to study the Interference fit of a superconducting magnet with an aluminium former. The magnet studied was for a 3 dimensional vector rotate magnet and quenching of the magnet was suspected to be the fit of the magnet.  The result was subsequently used for other design of the magnet produced at Oxford Instruments.

%-dissertation -plasmon/neutrino oscillation,physics beyond the standard model
%-oxford sepnet placement,coding experience,


\closing{Sincerely yours,\\Ken Keong Lee}


%\encl{Curriculum vitae, employment form} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}