\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{Laura Vanhoefer\\E-mail: lvanhoef@mpp.mpg.de}

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Laura Vanhoefer,} 
 
I am writing this letter to express my interest in the research project at Max Planck Institute for Physics advertised on the RISE research internship skim. I am a 3rd year Mphys Student at University of Southampton, UK as an international student there. 

I have done a placement during the summer of my 2nd year at Oxford Instruments near Abingdon,UK working on an independent student project on the shrink fitting of NiTi magnet with an aluminium mould. For that placement i have to work independently with the supervision of a supervisor therefore i would feel that my ability is sufficient for this internship. Though i do not have any in depth experience in programming, i did learn python in my university and quite familiar with unix interface devices as i did a crash course on it quite a while ago. However i believe with a proper guidance and tools i would be able to pick new programming skills within a few days. However those are not the main reason I applied to this internship but because this particular topics interest me deeply as I recently did a individual dissertation topic on neutrino oscillation where I did come across journals about atmospheric and solar neutrino. Though the discussion of my dissertation revolve more around the area of particle physics beyond the Standard Model, I could see how important such experiment could provide clue on the matter of neutrino oscillation in regarding expanding the Standard Model.
 
However from the advert i saw on rise website that the internship starts in late May which falls during my exams period and i hope this can be discuss in future if i get this internship. I have no prior knowledge of any german language and hope you could take note of this. I could be reach on kkl2g12@soton.ac.uk or hareyakana@hotmail.com if interview is needed to be arranged. Thank you for reading my applications.

\closing{Sincerely yours,\\Ken Keong Lee}


%\encl{Curriculum vitae, employment form} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}